A pipeline to analyse time-course gene expression data

### 2019-05-13 scripts/manuscript.Rmd
Added TODO items

- Add legends to the plots that don't have.
- Currently have two functions "plot_genes", "plot_centroids", that do exactly
  the same thing. Find a better name for both of them

@@

>>>>

- Add legends to the plots that don't have.
- Currently have two functions "plot_genes", "plot_centroids", that do exactly
  the same thing. Find a better name for both of them
- switch to camel case function names
- shorten function names
- Remove the namespace call
- Move the normalization to a supplementary data
- Make clear that it applies to RNASeq and how to call the different functions
  to RNASeq
- Check that clustering can deal with count data.

@@

**Add a helper function to make the contrasts for timely DE**
